Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-22 WSSSPE1_report/WSSSPE1_summary_report.tex
Clean up notes.

\title[]{Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)
\note{\scriptsize Authors, please add/check middle initials and affiliations}}

@@

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%
\thanks{{}$^{(3)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(4)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(5)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(6)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ Scientific Computing Group, Kitware, Inc.,  Clifton Park, NY, USA; \url{marcus.hanwell@kitware.com}}
%
\thanks{{}$^{(8)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(9)}$ Research Software Development Team, University College London, London, UK; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(10)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
%
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

@@

\section{Keynotes \note{lead: Sou-Cheng (Terrya) Choi}} \label{sec:keynotes}

@@

\section{Developing and Supporting Software \note{\scriptsize lead: Marcus Hanwell, contributor: Suresh Marru}} \label{sec:devel}

@@

\section{Policy \note{lead: Colin Venters, contributors: James Howison, Hilmar Lapp}} \label{sec:policy}

@@

\section{Communities \note{\vspace{-1ex}\tiny lead: Matthew Turk, contributors: Nancy Wilkins-Diehr, Chris Mattmann, Suresh Marru, Frank L\"{o}ffler, Andy Terrel}} \label{sec:community}

@@

\subsection{Defining Sustainability \note{lead: Daniel S. Katz}}  \label{sec:defining-sustainability}

@@

Table~\ref{tab:defining-sustainability} reproduces a summary created
by C.~Lenhardt ~\cite{lenhardt-wssspe1-panel}, which shows for each contribution to the
Modeling Sustainability panel what it meant when referring to
software, how it defined software sustainability, and which
approach it suggested to understand or evaluate sustainability.
\begin{table}[t]
  \begin{scriptsize}
    \begin{center}
      \caption{Summary of Modeling Sustainability papers from Policy Panel.  Adapted from~\cite{lenhardt-wssspe1-panel}.}
      \label{tab:defining-sustainability}
      \begin{tabular}{|p{2.3cm}|p{3.6cm}|p{4.4cm}|p{4.8cm}|}
                \hline
{\bf Paper/Authors}
& {\bf Software}
& {\bf Sustainability}
& {\bf Approach to Understand or Evaluate Sustainability} \\
                \hline
Calero, et al.~\cite{Calero_WSSSPE}
& General notion of software. Not explicitly defined.
& Sustainability is linked to quality.
& Add to ISO \\
                \hline
Venters, et al.~\cite{Venters_WSSSPE}
& Software as science software; increasingly complex; service-oriented computing
& Extensibility, interoperability, maintainability, portability, reusability, scalability, efficiency
& Use various architecture evaluation approaches to assess sustainability \\
                \hline
Pierce, et al.~\cite{Pierce_WSSSPE}
& Cyberinfrastructure software
& Sustainable to the extent to which there is a community to support it
& Open community governance \\
                \hline
Katz and Proctor~\cite{Katz_WSSSPE}
& E-research infrastructures (i.e. cyberinfrastructure)
& Persisting over time, meeting original needs and projected needs
& Equates models for the creation of software with sustaining software \\
                \hline
Lenhardt, et al.~\cite{Lenhardt_WSSSPE}
& Broadly defined as software supporting science
& Re-use; reproducible science
& Comparing data management life cycle to software development life cycle \\
                \hline
Weber, et al.~\cite{Weber_WSSSPE}
& Software broadly defined; a software ecosystem
& Software niches
& Ecological analysis and ecosystem \\
                \hline
     \end{tabular}
    \end{center}
  \end{scriptsize}
\end{table}

\subsection{Career Paths for Scientific Software Developers} \note{lead: Daniel S. Katz} \label{sec:career-tracks}

@@

\todo{anyone who needs to put something in here should}

@@

\section{Attendees \note{lead: Shel Swenson}} \label{sec:attendees}

>>>>

\title[]{Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)}
%\note{\scriptsize Authors, please add/check middle initials and affiliations}

@@

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%
\thanks{{}$^{(3)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(4)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(5)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(6)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ Scientific Computing Group, Kitware, Inc.,  Clifton Park, NY, USA; \url{marcus.hanwell@kitware.com}}
%
\thanks{{}$^{(8)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(9)}$ Research Software Development Team, University College London, London, UK; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(10)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
%
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA, USA; \url{gbb@ipac.caltech.edu}}
%
\thanks{{}$^{(14)}$ xxx}

@@

\section{Keynotes } \label{sec:keynotes} %\note{lead: Sou-Cheng (Terrya) Choi}

@@

\section{Developing and Supporting Software} \label{sec:devel}%\note{\scriptsize lead: Marcus Hanwell, contributor: Suresh Marru}

@@

\section{Policy} \label{sec:policy}%\note{lead: Colin Venters, contributors: James Howison, Hilmar Lapp}

@@

\section{Communities} \label{sec:community}%\note{lead: Matthew Turk, contributors: Nancy Wilkins-Diehr, Chris Mattmann, Suresh Marru, Frank L\"{o}ffler, Andy Terrel}

@@

\subsection{Defining Sustainability}  \label{sec:defining-sustainability}%\note{lead: Daniel S. Katz}

@@

Table~\ref{tab:defining-sustainability} reproduces a summary created
by C.~Lenhardt ~\cite{lenhardt-wssspe1-panel}, which shows for each contribution to the
Modeling Sustainability panel what it meant when referring to
software, how it defined software sustainability, and which
approach it suggested to understand or evaluate sustainability.
\begin{table}[t]
  \begin{scriptsize}
    \begin{center}
      \caption{Summary of Modeling Sustainability papers from Policy Panel.  Adapted from~\cite{lenhardt-wssspe1-panel}.}
      \label{tab:defining-sustainability}
      \begin{tabular}{|p{2.3cm}|p{3.6cm}|p{4.4cm}|p{4.8cm}|}
                \hline
{\bf Paper/Authors}
& {\bf Software}
& {\bf Sustainability}
& {\bf Approach to Understand or Evaluate Sustainability} \\
                \hline
Calero, et al.~\cite{Calero_WSSSPE}
& General notion of software. Not explicitly defined.
& Sustainability is linked to quality.
& Add to ISO \\
                \hline
Venters, et al.~\cite{Venters_WSSSPE}
& Software as science software; increasingly complex; service-oriented computing
& Extensibility, interoperability, maintainability, portability, reusability, scalability, efficiency
& Use various architecture evaluation approaches to assess sustainability \\
                \hline
Pierce, et al.~\cite{Pierce_WSSSPE}
& Cyberinfrastructure software
& Sustainable to the extent to which there is a community to support it
& Open community governance \\
                \hline
Katz and Proctor~\cite{Katz_WSSSPE}
& E-research infrastructures (i.e. cyberinfrastructure)
& Persisting over time, meeting original needs and projected needs
& Equates models for the creation of software with sustaining software \\
                \hline
Lenhardt,~et~al.~\cite{Lenhardt_WSSSPE}
& Broadly defined as software supporting science
& Re-use; reproducible science
& Comparing data management life cycle to software development life cycle \\
                \hline
Weber, et al.~\cite{Weber_WSSSPE}
& Software broadly defined; a software ecosystem
& Software niches
& Ecological analysis and ecosystem \\
                \hline
     \end{tabular}
    \end{center}
  \end{scriptsize}
\end{table}

\subsection{Career Paths for Scientific Software Developers}\label{sec:career-tracks} %\note{lead: Daniel S. Katz}

@@

%\todo{anyone who needs to put something in here should}

@@

\section{Attendees} \label{sec:attendees}  %\note{lead: Shel Swenson}
